How residence time constrains diversity

### 2015-06-20 paper/Manuscript.Rmd
finishing up Results -KL

*Autocorrelated residence times and right-skewed residence time distributions——*As expected, residence times of individuals, resource particles, inert tracers, and most any non-permanent component of the system were highly correlated. Right-skewed distributions characterized the life history of individuals, the presence of resource particles, and the tenure of species and traits (Figure ?). Residence time distributions were generally well approximated by lognormal and power-law models (e.g. Pareto, Zipf, Zipf-Mandelbrot).

@@

@@

## Conclusion

@@

```{r, results = 'hide', message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_June/18_June_3/SimData.csv")  
sim.data <- subset(sim.data, motion == ' fluid ')
```

>>>>

*Autocorrelated residence times and right-skewed residence time distributions—*The probabilistic and complex modeling approach produced all primary expected results, signifying that predictions of otherwise simplistic and idealized chemostat theory could arise in a complex system. Residence times of individuals, resource particles, inert tracers, and most any non-permanent component of the system were highly correlated (Fig 1). Likewise, residence time distributions were right-skewed and well approximated by lognormal and power-law models (e.g. Pareto, Zipf, Zipf-Mandelbrot) (Fig 2). We also observed the expected  hump-shaped relationship of *N* to residence time, revealing that residence time could be low enough to exclude reproduction and high enough to result in a rate of resource supply that could not support optimal growth.

@@

*Total abundance (N)*—

@@

## Conclusion/Discussion

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_June/18_June_3/SimData.csv")  
sim.data <- subset(sim.data, motion == ' fluid ')
```
